---
title: "My Amazing Article"
description: |
  Other cool stuff
author:
  - name: Michael Clark
    url: https://m-clark.github.io
    affiliation: CSCAR
    affiliation_url: https://cscar.research.umich.edu/
date: '`r Sys.Date()`'
output:
  distill::distill_article:
    highlight: default
    highlight_downlit: FALSE
    toc: true
# css: docs/style.css
bibliography: biblio.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = T, 
  eval      = T, 
  message   = F, 
  warning   = F, 
  comment   = NA,
  R.options = list(width = 120),
  cache.rebuild = F,
  cache = T,
  fig.align = 'center',
  fig.asp = .7,
  dev = 'svg',
  dev.args = list(bg = 'transparent')
)

library(tidyverse)
```


# Introduction


# Part 1: Basics

## Code

Time for code!  Already looks nice! By default, highlighting is done using colors optimized for accessibility and color contrast.

```{r}
library(tidyverse)

x = rlogis(1000)

qplot(sort(x), plogis(sort(x)), ylab = 'Probability', geom = 'line')
```

## Visualization


```{r}
library(leaflet)

leaflet(options = leafletOptions(minZoom = 2, maxZoom = 15)) %>%
  setView(lng  = 174.768,
          lat  = -36.852,
          zoom = 10) %>%
  addTiles() %>%
  addMarkers(lng   = 174.768,
             lat   = -36.852,
             popup = "The birthplace of R")
```

### Distill Layouts

- l-body
- l-body-outset
- l-page
- l-screen


Note: You will probably never remember these names.



```{r, layout = 'l-body-outset'}
library(leaflet)

leaflet(options = leafletOptions(minZoom = 2, maxZoom = 15)) %>%
  setView(lng  = 174.768,
          lat  = -36.852,
          zoom = 10) %>%
  addTiles() %>%
  addMarkers(lng   = 174.768,
             lat   = -36.852,
             popup = "The birthplace of R")
```
```{r, layout = 'l-page'}
library(leaflet)

leaflet(options = leafletOptions(minZoom = 2, maxZoom = 15)) %>%
  setView(lng  = 174.768,
          lat  = -36.852,
          zoom = 10) %>%
  addTiles() %>%
  addMarkers(lng   = 174.768,
             lat   = -36.852,
             popup = "The birthplace of R")
```
```{r, layout = 'l-screen'}
library(leaflet)

leaflet(options = leafletOptions(minZoom = 2, maxZoom = 15)) %>%
  setView(lng  = 174.768,
          lat  = -36.852,
          zoom = 10) %>%
  addTiles() %>%
  addMarkers(lng   = 174.768,
             lat   = -36.852,
             popup = "The birthplace of R")
```



Control: Use the fig.asp chunk option to modify the aspect ratio.

```{r aspect-ratio-demo, fig.cap='test figure', layout = 'l-body-outset', fig.asp=.2}
library(leaflet)

leaflet(options = leafletOptions(minZoom = 2, maxZoom = 15)) %>%
  setView(lng  = 174.768,
          lat  = -36.852,
          zoom = 10) %>%
  addTiles() %>%
  addMarkers(lng   = 174.768,
             lat   = -36.852,
             popup = "The birthplace of R")
```


Reference figures by chunk name, **as long as they also have a caption**.  For example, if the chunk is named 'aspect-ratio-demo', then `\@ref(fig:aspect-ratio-demo)` would reference it. For example, see figure \@ref(fig:aspect-ratio-demo).

# Part 2

## Citations

Create a file of your chosen type and point to it in the YAML.

Look at this citation- @clark-models, or these [@clark-pds; @clark-iml; @brms].

## Footnotes and asides

Here is a footnote[^footnote].  They can be clicked or just hovered over.

Asides are one of the best features of distill.

<aside> You never have to use parentheses again!</aside>





[^footnote]: Hey! It's a footnote!




